Historical Soil Organic Carbon Budget

### 2020-03-23 SOCbudgetPaper/methods.Rmd
Update methods.Rmd

## Agricultural management	(50) {#sec:agrimanagement}

@@

Our land use patterns are based on the Land-Use Harmonization 2 (LUH2, [@LUH2]) data set, which we aggregate from quarter degree to half degree resolution. To transform the five different cropland subcategories of LUH2 into our crop functional types we define country and year specific area shares based on FAOSTAT data ([@FAOSTAT]) (see \@ref(appendix:fao2luh2mag). Where no data is available we fill data gaps by using similar countries as proxies or global averages. Land use transitions are calculated as area differences of the land use data, allowing any land use type to either expand or shrink in each time step.

### Crop Production and Residues	(300)
Using half-degree yield data from LPJmL ([@LPJmL4_1]) as well as half-degree cropland pattern (see \@ref(#sec:landuse)) we compile crop functional type specific half-degree production patterns. We calibrate them to country level FAOSTAT production ([@FAOSTAT]) values to be in line with historical observations.

Starting from this harvested fraction we calculate above ground and below ground residual biomass using harvest indices and shoot:root ratios as described in ([@bodirsky2012]). We assume that all below ground biomass is left on the fields, whereas above ground biosmass can be drawn away for other purposes such as feeding animals ([@weindl]), fuel or for material uses. We calculate recycle shares by subtracting all residue usages (see [@bodirsky1012]) from the total above ground biomass.

<!-- Add formular or drawings here? -->

<!-- Ask benni if it is ok to just cide his paper here and not go into detail, how we distribute the residues -->

To transform dry matter values into carbon quantities used as soil input, we compiled crop functional type specific carbon to dry matter (c:dm) ratios for harvested organs and applied a universal c:dm ratio of 0.44 for all above and below ground residue biomass.

>>>>

## Agricultural management data on 0.5 degrees	(50) {#sec:agrimanagement}

@@

Land use patterns are based on the Land-Use Harmonization 2 (LUH2, [@LUH2]) data set, which we aggregate from quarter degree to half degree resolution. We disaggregate the five different cropland subcategories of LUH2 into our X crop groups, assuming relative shares for each gridcell based on the country and year specific area shares of FAOSTAT data ([@FAOSTAT]) (see \@ref(appendix:fao2luh2mag)<!--glaube nicht dass du da noch n appendix brauchst-->. For X countries without FAOSTAT data, we fill data gaps by using similar countries as proxies or global averages<!--heisst das die haben HURTT data aber keine FAO daten? woher kriegt dann hurtt die daten?-->. Land use transitions are calculated as area differences of the land use data.

### Crop Production and Residues	(300)
Using half-degree yield data from LPJmL ([@LPJmL4_1]) as well as half-degree cropland patterns (see \@ref(#sec:landuse)) we compile crop functional type specific half-degree production patterns. We calibrate cellular yields with one country-level calibration factor for each crop-group to meet historical FAOSTAT production ([@FAOSTAT]).

Starting from these production estimates of the harvested organs and their respective crop area, we estimate above-ground and below-ground residual biomass using yield-dependent harvest indices and shoot:root ratios as described in ([@bodirsky2012]). We assume that all below ground biomass is left on the fields. A fixed share of the above-ground residues is assumed to be burnt on field, which depends on the per-capita income of the country. For low-income countries according to worldbank definitions (<1000 USD/yr), we assume a ... etc.
ground biomass can be burned or harvested for other purposes such as feeding animals ([@weindl]), fuel or for material uses. We calculate recycle shares by subtracting all residue usages (see [@bodirsky1012, @weindl2019]) from the total above ground biomass.

<!-- Add formular or drawings here? --> 
<!-- if you want, but first finish the rest -->
<!-- Ask benni if it is ok to just cite his paper here and not go into detail, how we distribute the residues --> <!-- Benni: No, explain in detail as it is important for your manuscript and adds credibility to your detailed calcualtions. Also, some assumptions may have changed (e.g. DevelopmentState as function of gdp) -->

To transform dry matter estimates into carbon, we compiled crop functional type specific carbon to dry matter (c:dm) ratios (see appendix table X) [citations] for harvested organs and applied a universal c:dm ratio of 0.44 [citation] for all above and below ground residue biomass.
